Tulai

### 2023-10-06 paper/paper.qmd
resolve merge conflict

```{r}
# SS: get the contributions of each variable to the first two principal components, which we can then use in the text.

@@

```{r}
# screeplot; inspect distribution of PCs
fviz_screeplot(res.pca)
```

@@

# Display the table
kable_output 
```

>>>>

# SS: get the contributions of each variable to the first two principal components, which we can then use in the text.

@@

# screeplot; inspect distribution of PCs
fviz_screeplot(res.pca)
```

@@

# Display the table

kable_output
